---
title: "FJD Fines and Costs Analysis (10-27-2017)"
author: "Michael Hollander / CLS"
date: "October 29, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

```{r includes}
source("processFinesCosts.R")
```

### Basic Statistics About the FJD Fines and Costs Data
Category | All Cases | Active Cases | Referred Cases
---------|-----------|-----------|-----------
Total Entries | `r totalEntries` | `r totalActive` (`r 100*round(totalActive/totalEntries,2)`%)| `r totalReferred`  (`r 100*round(totalReferred/totalEntries,2)`%)
Total Unique Names | `r totalUniqueNames` 
Cases with No Valid Address | `r totalNoAddress` | `r totalNoAddressActive` (`r 100*round(totalNoAddressActive/totalNoAddress,2)`%)| `r totalNoAddressReferred` (`r 100*round(totalNoAddressReferred/totalNoAddress,2)`%)
Total Amount Owed | `r paste("$",totalOwed)` | `r paste("$",totalOwed-totalOwedReferred)` (`r 100*(1-round(totalOwedReferred/totalOwed,2))`%) |`r paste("$",totalOwedReferred)` (`r 100*round(totalOwedReferred/totalOwed,2)`%)
Total Amount Delinquent | $`r totalDelinquent`| $`r totalDelinquent-totalDelinquentReferred` (`r 100*round(1-totalDelinquentReferred/totalDelinquent,2)`%)| $`r totalDelinquentReferred` (`r 100*round(totalDelinquentReferred/totalDelinquent,2)`%)
Median Monthly Payment | `r paste("$", median(fcdata$MonthlyPayment))` | `r paste("$", summariseFcdata$MonthlyPayment[summariseFcdata$Status=="Active"])` | `r paste("$", summariseFcdata$MonthlyPayment[summariseFcdata$Status=="Referred"])`
Median months in Arrears | `r median(fcdata$MonthlyPaymentsBehindRounded[fcdata$MonthlyPayment > 0])` | `r summariseFcdata$MonthlyPaymentsBehindRounded[summariseFcdata$Status=="Active"]` | `r summariseFcdata$MonthlyPaymentsBehindRounded[summariseFcdata$Status=="Referred"]`


### Some Plots
This first plot just shows the overall distribution of total amount owed (not in arrears) by individuals with payment plans, categorized by whether the case has been referred to a collection agency or not.  What we can see is that active cases tend to be for smaller amounts of money than referred cases, although it also shows that some cases have been referred despite no money being owed. What I don't know and what would be interesting to find out is: if a case is referred to a collection agency, is the entire amount referred or just the portion in arrears?  If the former is true, it makes sense that higher total value cases would end up in collections as they are more attractive to the collections agency, which gets an additional 25% on top of what is paid to it for the court.    
```{r plot1}
plotTotalOwed
```

***

This plot shows the distribution of the amount delinquent for individuals with payment plans, categorized by whether the case has been referred to a collection agency or not.  Like the first graph, the cases that have been referred owed more than the active cases.  FWIW, there is a larger gap between the median in arrears for each category ($ `r summariseFcdata$DelinquentAmount[summariseFcdata$Status=="Referred"] - summariseFcdata$DelinquentAmount[summariseFcdata$Status=="Active"]` ) vs the median owed ($ `r summariseFcdata$TotalOwed[summariseFcdata$Status=="Referred"] - summariseFcdata$TotalOwed[summariseFcdata$Status=="Active"]`).
```{r plot2}
plotDelinquentAmount
```

***

This plot shows the monthly payment owed by people in each category.  Interestingly enough, collection agency cases have a lower payment plant ($`r summariseFcdata$MonthlyPayment[summariseFcdata$Status=="Referred"]` vs $`r summariseFcdata$MonthlyPayment[summariseFcdata$Status=="Active"]`), which suggests that people who have been sent to a collection agency have also previously demonstrated a lower ability to pay.  Worth noting is that these graphs are fairly useless - there are **HUGE** spikes that I am not showing at $25 and $35, since almost everyone is in a plan of this amount.
```{r plot3}
plotMonthlyPayment
```

***
Finally we can see the real difference between people who have been referred to collections and those who have not: those who have been referred to collections are MANY more months behind in their payments (`r summariseFcdata$MonthlyPaymentsBehind[summariseFcdata$Status=="Referred"]` vs `r summariseFcdata$MonthlyPaymentsBehind[summariseFcdata$Status=="Active"]`), regardless of total owed.
```{r plot4}
plotMonthlyPaymentsBehind
```

*** 
We can see that for any given number of months in arrears, there is no difference in the delinquent amount owed to the court, however.  The median amount owed at any given number of months behind is virtually identical for active and referred cases (at least up to about 134 months behind where things go wacky).  The median amount behind, in case you are wondering, is $25 * number of months.
```{r plot5}
plotDelinquentPerPaymentsBehind
```

***
The same effect seems to be true when we plot median amount owed (not in arrears, just owed overall) vs the number of months in arrears.  The scale of this plot is slightly different, but if you look at the numbers, the median amount owed at any given level is virtually identical to the median amount in arrears.  In other words, most people owe the entire amount of their payment plan.  
```{r plot6}
plotOwedPerPaymentsBehind
```