---
title: "FJD Fines and Costs Analysis (10-27-2017)"
author: "Michael Hollander / CLS"
date: "October 29, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

```{r includes}
source("processFinesCosts.R")
```

### Basic Statistics About the FJD Fines and Costs Data
Category | Statistic
---------|-----------
Total Entries | `r totalEntries`
Total Unique Names | `r totalUniqueNames`
Total Amount Owed | `r paste("$",totalOwed)`
Total Amount Delinquent | `r paste("$",totalDelinquent)`
Median Monthly Payment | `r paste("$", median(fcdata$MonthlyPayment))`
Median months in Arrears | `r median(fcdata$MonthlyPaymentsBehind[fcdata$MonthlyPayment > 0])`

### Statistics Broken Down By Active vs Referred Cases
Category | Statistic
---------|-----------
Total Active |  `r totalActive`
Total Referred to Collections | `r totalReferred`
Total Amount Owed Active Cases | `r paste("$",totalOwed-totalOwedReferred)`
Total Amount Owed Referred Cases | `r paste("$",totalOwedReferred)`
Total Amount Delinquent Active Cases | `r paste("$",totalDelinquent-totalDelinquentReferred)`
Total Amount Delinquent Referred Cases | `r paste("$",totalDelinquentReferred)`
Median Monthly Payment Plan Active | `r paste("$", summariseFcdata$MonthlyPayment[summariseFcdata$Status=="Active"])`
Median Monthly Payment Plan Referred | `r paste("$", summariseFcdata$MonthlyPayment[summariseFcdata$Status=="Referred"])`
Median Months in Arrears Active | `r summariseFcdata$MonthlyPaymentsBehind[summariseFcdata$Status=="Active"]`
Median Months in Arrears Referred | `r summariseFcdata$MonthlyPaymentsBehind[summariseFcdata$Status=="Referred"]`

### Some Plots
```{r plot1}
plotTotalOwed
```

***

```{r plot2}
plotDelinquentAmount
```

***

```{r plot3}
plotMonthlyPayment
```

***

```{r plot4}
plotMonthlyPaymentsBehind
```
